Pillar 1 - Student Topic Profile

### 2019-04-30 Pillar 1 - Topic Profile.Rmd

```{r load, cache.lazy = TRUE}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/course_current.RDATA")

@@

# Course topic profile
```{r gamma_spread}
gamma        <- topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
gamma_spread <- gamma %>% spread(topic, gamma)

beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
```

@@

Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).

@@

@@

Topic chosen by model are related to the course.
```{r}
beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)

>>>>

```{r load, cache.lazy = TRUE}
#load("App/Recommender System/topic_model_gb.RDATA")
load("App/Recommender System/data_topic_models.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/course_current.RDATA")

@@

# Course topic profile
```{r gamma_spread}
gamma        <- app_model$Gamma %>% .[[1]] %>% mutate(topic = topic %>% str_replace(" ", "_"))  #topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
gamma_spread <- gamma %>% spread(topic, gamma)

beta <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta) #topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
```

@@

Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).
#Save
```{r save student_TP}
save(student_TP, file = "./App/Recommender System/student_TP.RDATA")
```

@@

```{r}
save(fit_lasso, file = "Output/CV.RDATA")
```

@@

Topic chosen by model are related to the course.
```{r}
beta <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta)
#beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
